\sout{A smart street lighting system based on \rev{an} IPv6-enabled wireless sensor network} \rev{A routing protocol for an urban IoT based on a smart streetlighting wireless sensor network}

### 2014-12-17 2014_ELSEVIER_CEE_SI/paper_cee_special_issue.tex
pequena alteração no abstract

\begin{abstract}
%% Text of abstract
In this paper, we propose a \rev{routing protocol} for a smart street lighting system based on IPv6-enabled wireless sensor network. We discuss the main drawbacks of \rev{the} RPL \rev{(IPv6 Routing Protocol for
Low-Power and Lossy Networks)} \sout{routing protocol} for P2P \rev{(point-to-point)} communication in large-scale 6LoWPAN networks. Then, we address such drawbacks by proposing a new routing algorithm, named \textit{GeoRank}, which integrates RPL protocol with \sout{GOAFR} the position-based routing protocol, \rev{called GOAFR (Greedy Other Adaptive Face Routing)}. Simulations were performed on networks extracted from real street maps. The obtained results show that \textit{GeoRank} finds shorter routes than RPL in high link density conditions and than GOAFR in low link density conditions. Thus, \textit{GeoRank} shows to be adaptive to variable link densities found in large-scale networks. Further, \textit{GeoRank} avoids the use of bandwidth-consuming control messages required in RPL, while being more scalable in terms of memory usage than storing-mode RPL.
\end{abstract}

>>>>

\begin{abstract}
%% Text of abstract
In this paper, we propose a \rev{routing protocol} for a smart street lighting system based on IPv6-enabled wireless sensor network. We discuss the main drawbacks of \rev{the} RPL \rev{(IPv6 Routing Protocol for
Low-Power and Lossy Networks)} \sout{routing protocol} for P2P \rev{(point-to-point)} communication in large-scale 6LoWPAN networks. Then, we address such drawbacks by proposing a new routing algorithm, named \textit{GeoRank}, which integrates RPL protocol with \sout{GOAFR} the position-based routing protocol \rev{GOAFR (Greedy Other Adaptive Face Routing)}. Simulations were performed on networks extracted from real street maps. The obtained results show that \textit{GeoRank} finds shorter routes than RPL in high link density conditions and than GOAFR in low link density conditions. Thus, \textit{GeoRank} shows to be adaptive to variable link densities found in large-scale networks. Further, \textit{GeoRank} avoids the use of bandwidth-consuming control messages required in RPL, while being more scalable in terms of memory usage than storing-mode RPL.
\end{abstract}
